---
title: 
output:
  revealjs::revealjs_presentation:
    theme: night
    transition: fade
    highlight: zenburn
    center: true
---



## Finding Social Science Data for Your Research {data-background="data1.jpg"}

Josh Quan

Tisch Library

Spring 2017



##

> An approximate answer to the right question is worth a
great deal more than a precise answer to the wrong
question.

-John Tukey



## Plan your Research with a Literature Review {data-background="books.jpg"}

http://tischlibrary.tufts.edu



## Ask Yourself... {data-background="books.jpg"}



- How feasible or doable is your research question? 

- Can you answer the question with a simple descriptive statistic (like an average, median, percentage, etc)? If so, then your research question might be too narrow.

- Does the answer to your question have too many angles? For example: What best practices have solved poverty? If so, then your question might be too broad.
		


## The structure and availability of data



| Unit of Analysis                                                                       	| Geography                                                                          	| Time-Period                                                             	| Frequency                                                                                              	|
|----------------------------------------------------------------------------------------	|------------------------------------------------------------------------------------	|-------------------------------------------------------------------------	|--------------------------------------------------------------------------------------------------------	|
| For which level do you want data?  Summary or Micro?  (individuals, counties, nations) 	| Is there a geographic  component to your topic?  (U.S., Sub-Saharan Africa, India) 	| Do you want a data for a  specific time period?  (1980-2000, 1930-1960) 	| How often do you want measures  for your variables?  (every year, every ten years, monthly, quarterly) 	|


## Data Providers

| Researchers                                                    	| Government Agencies                                                                                                                                                                       	| NGOs                                                                                                                                     	| Research Organizations                                                                                                   	|
|----------------------------------------------------------------	|-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------	|------------------------------------------------------------------------------------------------------------------------------------------	|--------------------------------------------------------------------------------------------------------------------------	|
| Are there people you know who are doing this kind of research? 	| Think about government agencies - is the request for some official statistics or data that they'd be likely to collect and publish? (industry, agriculture, construction, disease, crime) 	| Are there councils or interest organizations devoted to the topic that might collect data independently? (HIV/AIDS, drugs, civil rights) 	| Would any specific research organizations be interested in the topic? (Pew, Roper, Gallup, NORC, NBER, World Bank, OECD) 	|



##Data Research Guide

http://researchguides.library.tufts.edu/data



##Web Scraping
http://statbel.fgov.be/en/statistics/figures/economy/indicators/prix_prod_con/

```{r, include=FALSE}
library(rvest)
```

```{r, warning=FALSE, message=FALSE}
url='http://statbel.fgov.be/en/statistics/figures/economy/indicators/prix_prod_con/'
TAB=read_html(url)%>%html_nodes('td')%>%html_text()
NAMES=read_html(url)%>%html_nodes('th')%>%html_text()
M=data.frame(matrix(TAB,ncol=5,nrow=9,byrow=T))
M=cbind(NAMES[7:15],M)
names(M)=NAMES[1:6]
M
```


##DataLab 

https://sites.tufts.edu/datalab/


## questions?

email: joshua.quan@tufts.edu


<!--render("index.Rmd", revealjs_presentation())-->

